Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-10-09 manuscript/manuscript.Rmd
try excel data format

---
title: "Estimating the replicability of psychology experiments after an initial failure to replicate"
author:
  - name: Veronica Boyce
    affiliation: Psych
    footnote:
      - corresp
  - name: Ben Prystawski
    affiliation: Psych
  - name: Adani B. Abutto
    affiliation: Psych
  - name: Emily M. Chen
    affiliation: Psych
  - name: Ziwen Chen
    affiliation: GSB
  - name: Howard Chiu
    affiliation: Edu
  - name: Irmak Ergin
    affiliation: Psych
  - name: Anmol Gupta
    affiliation: Psych
  - name: Chuqi Hu
    affiliation: Symsys
  - name: Bendix Kemmann
    affiliation: Philosophy
  - name: Nastasia Klevak
    affiliation: Psych
  - name: Verity Y. Q. Lua
    affiliation: Psych
  - name: Mateus M. Mazzaferro
    affiliation: Edu
  - name: Khaing Mon
    affiliation: Symsys
  - name: Dan Ogunbamowo
    affiliation: Psych
  - name: Alexander Pereira
    affiliation: [Psych, Philosophy]
  - name: Jordan Troutman
    affiliation: CS
  - name: Sarah Tung
    affiliation: Psych
  - name: Raphael Uricher
    affiliation: Psych
  - name: Michael C. Frank
    affiliation: Psych
address:
  - code: Psych
    address: Department of Psychology, Stanford University
  - code: GSB
    address: Graduate School of Business, Stanford University
  - code: Edu
    address: Graduate School of Education, Stanford University
  - code: Symsys
    address: Symbolic Systems Program, Stanford University
  - code: Philosophy
    address: Department of Philosophy, Stanford University
  - code: CS
    address: Department of Computer Science, Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: apa7.csl # Use any CSL
nocite: |
  @krauss2003, @ngo2019, @todd2016, @jara-ettinger2022, @porter2016, @birch2007, @child2018, @chou2016, @craig2014, @gong2019, @haimovitz2016, @hopkins2016, @paxton2012, @payne2008, @schechtman2010, @tarampi2016, @yeshurun2003
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt
header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,chains}
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

@@

@gong2019 looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
The first replication sampled US adults and did not find a significant interaction.
The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
The rescue did not recover the interaction.

>>>>

---
title: "Estimating the replicability of psychology experiments after an initial failure to replicate"
author:
  - Anonymous
# author:
#   - name: Veronica Boyce
#     affiliation: Psych
#     footnote:
#       - corresp
#   - name: Ben Prystawski
#     affiliation: Psych
#   - name: Adani B. Abutto
#     affiliation: Psych
#   - name: Emily M. Chen
#     affiliation: Psych
#   - name: Ziwen Chen
#     affiliation: GSB
#   - name: Howard Chiu
#     affiliation: Edu
#   - name: Irmak Ergin
#     affiliation: Psych
#   - name: Anmol Gupta
#     affiliation: Psych
#   - name: Chuqi Hu
#     affiliation: Symsys
#   - name: Bendix Kemmann
#     affiliation: Philosophy
#   - name: Nastasia Klevak
#     affiliation: Psych
#   - name: Verity Y. Q. Lua
#     affiliation: Psych
#   - name: Mateus M. Mazzaferro
#     affiliation: Edu
#   - name: Khaing Mon
#     affiliation: Symsys
#   - name: Dan Ogunbamowo
#     affiliation: Psych
#   - name: Alexander Pereira
#     affiliation: [Psych, Philosophy]
#   - name: Jordan Troutman
#     affiliation: CS
#   - name: Sarah Tung
#     affiliation: Psych
#   - name: Raphael Uricher
#     affiliation: Psych
#   - name: Michael C. Frank
#     affiliation: Psych
# address:
#   - code: Psych
#     address: Department of Psychology, Stanford University
#   - code: GSB
#     address: Graduate School of Business, Stanford University
#   - code: Edu
#     address: Graduate School of Education, Stanford University
#   - code: Symsys
#     address: Symbolic Systems Program, Stanford University
#   - code: Philosophy
#     address: Department of Philosophy, Stanford University
#   - code: CS
#     address: Department of Computer Science, Stanford University
#footnote:
#  - code: corresp
#    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: apa7.csl # Use any CSL
nocite: |
  @krauss2003, @ngo2019, @todd2016, @jara-ettinger2022, @porter2016, @birch2007, @child2018, @chou2016, @craig2014, @gong2019, @haimovitz2016, @hopkins2016, @paxton2012, @payne2008, @schechtman2010, @tarampi2016, @yeshurun2003
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt
header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,chains}
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Conflicts of Interest {.unnumbered}

The authors report no conflicts of interest.

@@

@gong2019 looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
The first replication sampled US adults and did not find a significant interaction.
The rescuer thought that cultural differences may have played a role and specifically sampled adults who reported their ethnicity as East Asian.
The rescue did not recover the interaction.

### 2024-10-09 manuscript/manuscript.tex
try excel data format

@@

% Create labels for Addresses if the are given by code
\MyNewLabel{ADDRTXT}{Psych}{Department of Psychology, Stanford University}
\MyNewLabel{ADDRTXT}{GSB}{Graduate School of Business, Stanford University}
\MyNewLabel{ADDRTXT}{Edu}{Graduate School of Education, Stanford University}
\MyNewLabel{ADDRTXT}{Symsys}{Symbolic Systems Program, Stanford University}
\MyNewLabel{ADDRTXT}{Philosophy}{Department of Philosophy, Stanford University}
\MyNewLabel{ADDRTXT}{CS}{Department of Computer Science, Stanford University}

% Create labels for Footnotes if they are given by code
\MyNewLabel{ANOTETXT}{corresp}{Corresponding author. Email: \href{mailto:vboyce@stanford.edu}{\nolinkurl{vboyce@stanford.edu}}}

@@

\createaddrlblbycode{Psych}

\createanotelblbycode{corresp}

\author[%
\addrlblbycode{Psych}%
,%
$\anotelblbycode{corresp}$%
]{Veronica Boyce}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Ben Prystawski}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Adani B. Abutto}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Emily M. Chen}

\addrbycode{Psych}

\createaddrlblbycode{GSB}

\author[%
\addrlblbycode{GSB}%
]{Ziwen Chen}

\addrbycode{GSB}

\createaddrlblbycode{Edu}

\author[%
\addrlblbycode{Edu}%
]{Howard Chiu}

\addrbycode{Edu}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Irmak Ergin}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Anmol Gupta}

\addrbycode{Psych}

\createaddrlblbycode{Symsys}

\author[%
\addrlblbycode{Symsys}%
]{Chuqi Hu}

\addrbycode{Symsys}

\createaddrlblbycode{Philosophy}

\author[%
\addrlblbycode{Philosophy}%
]{Bendix Kemmann}

\addrbycode{Philosophy}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Nastasia Klevak}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Verity Y. Q. Lua}

\addrbycode{Psych}

\createaddrlblbycode{Edu}

\author[%
\addrlblbycode{Edu}%
]{Mateus M. Mazzaferro}

\addrbycode{Edu}

\createaddrlblbycode{Symsys}

\author[%
\addrlblbycode{Symsys}%
]{Khaing Mon}

\addrbycode{Symsys}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Dan Ogunbamowo}

\addrbycode{Psych}

\createaddrlblbycode{Psych}
\createaddrlblbycode{Philosophy}

\author[%
\addrlblbycode{Psych}%
,%
\addrlblbycode{Philosophy}%
]{Alexander Pereira}

\addrbycode{Psych}
\addrbycode{Philosophy}

\createaddrlblbycode{CS}

\author[%
\addrlblbycode{CS}%
]{Jordan Troutman}

\addrbycode{CS}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Sarah Tung}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Raphael Uricher}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Michael C. Frank}

\addrbycode{Psych}

@@

\caption{\label{tab:tab-porig}$P$-original values between different sets of experiments. The primary analysis is between the original result and the meta-analytic aggregation of all replications. All $p$-original values assume an imputed heterogeneity value of $\tau$=.21.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
\cmidrule(l{3pt}r{3pt}){2-6}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
\midrule
Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
\bottomrule
\end{tabular}
\end{table}

@@

As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue (i.e.~excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
For a) the original versus the first replication and the rescue, the median value of \(p\)-original was 0.1 {[}IQR: 0.01 - 0.27{]}, and 35\% of the \(p\)-original values were less than .05.
For b) the original versus the rescue, the median value of \(p\)-original was 0.06 {[}IQR: 0.01 - 0.52{]}, and 47\% of the \(p\)-original values were less than .05.
For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0.01 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
For d) the rescue versus the other replications, the median value of \(p\)-original was 0.31 {[}IQR: 0.14 - 0.78{]}, and 24\% of the \(p\)-original values were less than .05.

@@

\caption{\label{tab:cor-table}Correlations between an individual predictor and the subjective replication score of the rescue project. The first set of predictors were pre-registered based on the correlates used in Boyce et al. (2023). Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent. For details about how the predictors were coded, see the Methods section of Boyce et al. (2023). The last three predictors were added post-hoc.}
\centering
\begin{tabular}[t]{rcc}
\toprule
Predictors & r & p\\
\midrule
Social & 0.133 & 0.612\\
Other psych & -0.295 & 0.250\\
Within subjects & 0.210 & 0.418\\
Single vignette & -0.030 & 0.910\\
Switch to online & 0.175 & 0.501\\
Open data & 0.231 & 0.373\\
Open materials & 0.471 & 0.057\\
Original authors at Stanford & -0.233 & 0.369\\
Log number of trials & 0.005 & 0.985\\
Log original sample size & 0.027 & 0.919\\
Log rescue/original sample size & 0.024 & 0.927\\
\midrule\\
Log replication sample size & -0.258 & 0.317\\
Log replication/original sample size & -0.487 & 0.048\\
Log rescue/replication sample size & 0.490 & 0.046\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:tab-size}Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.}
\centering
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{1}{c}{Paper} & \multicolumn{1}{c}{Score} & \multicolumn{3}{c}{N} & \multicolumn{2}{c}{closeness} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7}
 &  & Original & Replication & Rescue & Replication & Rescue\\
\midrule
Krauss \& Wang 2003 & 1.00 & 101 & 19 & 75 & close & very close\\
Ngo et al. 2019 & 1.00 & 31 & 12 & 77 & very close & very close\\
Todd et al. 2016 & 1.00 & 63 & 26 & 55 & very close & very close\\
Jara-Ettinger et al. 2022 & 0.75 & 144 & 147 & 426 & exact & exact\\
Porter et al. 2016 & 0.75 & 145 & 168 & 136 & close & close\\
Birch \& Bloom 2007 & 0.00 & 103 & 73 & 247 & very close & very close\\
Child et al. 2018 & 0.00 & 35 & 40 & 98 & very close & very close\\
Chou et al. 2016 & 0.00 & 100 & 158 & 252 & very close & very close\\
Craig \& Richeson 2014 & 0.00 & 121 & 76 & 127 & exact & exact\\
Gong et al. 2019 & 0.00 & 155 & 90 & 137 & far & far\\
Haimovitz \& Dweck 2016 & 0.00 & 132 & 97 & 141 & exact & exact\\
Hopkins et al. 2016 & 0.00 & 147 & 93 & 161 & very close & very close\\
Paxton et al. 2012 & 0.00 & 92 & 82 & 160 & close & close\\
Payne et al. 2008 & 0.00 & 48 & 23 & 23 & far & very close\\
Schechtman et al. 2010 & 0.00 & 22 & 20 & 21 & close & close\\
Tarampi et al. 2016 & 0.00 & 139 & 212 & 166 & close & very close\\
Yeshurun \& Levy 2003 & 0.00 & 18 & 10 & 18 & close & very close\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

Gong et al. (\citeproc{ref-gong2019}{2019}) looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
The first replication sampled US adults and did not find a significant interaction.
The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
The rescue did not recover the interaction.

>>>>

  pdfauthor={Anonymous},

@@

% Create labels for Addresses if the are given by code

% Create labels for Footnotes if they are given by code

@@

\author[%
]{}

@@

\caption{\label{tab:tab-porig}$P$-original values between different sets of experiments. The primary analysis is between the original result and the meta-analytic aggregation of all replications. All $p$-original values assume an imputed heterogeneity value of $\tau$=.21.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
\cmidrule(l{3pt}r{3pt}){2-6}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
\midrule
Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
Jara-Ettinger et al. 2022 & 0.009 & 0.009 & 0.000 & 0.004 & 0.000\\
Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
\bottomrule
\end{tabular}
\end{table}

@@

As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue (i.e.~excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
For a) the original versus the first replication and the rescue, the median value of \(p\)-original was 0.1 {[}IQR: 0.01 - 0.27{]}, and 35\% of the \(p\)-original values were less than .05.
For b) the original versus the rescue, the median value of \(p\)-original was 0.06 {[}IQR: 0.01 - 0.52{]}, and 47\% of the \(p\)-original values were less than .05.
For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
For d) the rescue versus the other replications, the median value of \(p\)-original was 0.31 {[}IQR: 0.14 - 0.78{]}, and 24\% of the \(p\)-original values were less than .05.

@@

\caption{\label{tab:cor-table}Correlations between an individual predictor and the subjective replication score of the rescue project. The first set of predictors were pre-registered based on the correlates used in Boyce et al. (2023). Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent. For details about how the predictors were coded, see the Methods section of Boyce et al. (2023). The last three predictors were added post-hoc.}
\centering
\begin{tabular}[t]{rcc}
\toprule
Predictors & r & p\\
\midrule
Social & 0.133 & 0.612\\
Other psych & -0.295 & 0.250\\
Within subjects & 0.210 & 0.418\\
Single vignette & -0.030 & 0.910\\
Switch to online & 0.175 & 0.501\\
Open data & 0.231 & 0.373\\
Open materials & 0.471 & 0.057\\
Original authors at Stanford & -0.233 & 0.369\\
Log number of trials & 0.005 & 0.985\\
Log original sample size & 0.027 & 0.919\\
Log rescue/original sample size & 0.024 & 0.927\\
\midrule\\
Log replication sample size & -0.261 & 0.311\\
Log replication/original sample size & -0.493 & 0.045\\
Log rescue/replication sample size & 0.493 & 0.044\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:tab-size}Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.}
\centering
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{1}{c}{Paper} & \multicolumn{1}{c}{Score} & \multicolumn{3}{c}{N} & \multicolumn{2}{c}{closeness} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7}
 &  & Original & Replication & Rescue & Replication & Rescue\\
\midrule
Krauss \& Wang 2003 & 1.00 & 101 & 19 & 75 & close & very close\\
Ngo et al. 2019 & 1.00 & 31 & 12 & 77 & very close & very close\\
Todd et al. 2016 & 1.00 & 63 & 26 & 55 & very close & very close\\
Jara-Ettinger et al. 2022 & 0.75 & 144 & 142 & 426 & exact & exact\\
Porter et al. 2016 & 0.75 & 145 & 168 & 136 & close & close\\
Birch \& Bloom 2007 & 0.00 & 103 & 73 & 247 & very close & very close\\
Child et al. 2018 & 0.00 & 35 & 40 & 98 & very close & very close\\
Chou et al. 2016 & 0.00 & 100 & 158 & 252 & very close & very close\\
Craig \& Richeson 2014 & 0.00 & 121 & 76 & 127 & exact & exact\\
Gong et al. 2019 & 0.00 & 155 & 90 & 137 & far & far\\
Haimovitz \& Dweck 2016 & 0.00 & 132 & 97 & 141 & exact & exact\\
Hopkins et al. 2016 & 0.00 & 147 & 93 & 161 & very close & very close\\
Paxton et al. 2012 & 0.00 & 92 & 82 & 160 & close & close\\
Payne et al. 2008 & 0.00 & 48 & 23 & 23 & far & very close\\
Schechtman et al. 2010 & 0.00 & 22 & 20 & 21 & close & close\\
Tarampi et al. 2016 & 0.00 & 139 & 212 & 166 & close & very close\\
Yeshurun \& Levy 2003 & 0.00 & 18 & 10 & 18 & close & very close\\
\bottomrule
\end{tabular}
\end{table}

@@

\section*{Conflicts of Interest}\label{conflicts-of-interest}
\addcontentsline{toc}{section}{Conflicts of Interest}

The authors report no conflicts of interest.

@@

Gong et al. (\citeproc{ref-gong2019}{2019}) looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
The first replication sampled US adults and did not find a significant interaction.
The rescuer thought that cultural differences may have played a role and specifically sampled adults who reported their ethnicity as East Asian.
The rescue did not recover the interaction.
